\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{ifthen}
\usepackage{setspace} 
\usepackage{multicol}
\usepackage[style=authoryear]{biblatex}
\addbibresource{publications.bib}
\usepackage{needspace}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!90!black,  
    urlcolor=blue!75!black,    
    citecolor=blue!60!black 
}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-5pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\titleformat{\subsection}{\vspace{-4pt}\scshape\raggedright\large}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeItemL}[1]{\item\small{{#1 \vspace{-5pt}}}}

\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}}

\newcommand{\resumeSubheadingT}[4]{\vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}}

\newcommand{\resumeSubheadingM}[5]{\vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{$\quad$ -\small #5} \\
    \end{tabular*}\vspace{-4pt}}

\newcommand{\resumeProjectHeading}[2]{\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=\textbullet]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\setlength{\footskip}{4.08003pt}

\begin{document}

\resumeSubHeadingListStart  % Start the main list

% Fleurish project
\resumeProjectHeading
{\href{https://github.com/knightwayne/HackTheNorth-2024}{\underline{\textbf{Fleurish}}} | Python, Flask, PostgreSQL}{}
\resumeItemListStart
\resumeItem{Developed a real-time video processing application using Python and Flask backend, integrating OpenCV for live video feed manipulation, and storing data in PostgreSQL.}
\resumeItem{Implemented asynchronous video frame processing with Flask, enabling concurrent user sessions and reducing latency; demonstrated at Hack The North 2024 with 30+ users simultaneously.}
\resumeItemListEnd

% ShopNode project
\resumeProjectHeading
{\href{https://github.com/knightwayne/Ecommerce-Website}{\underline{\textbf{ShopNode}}} | Python, Flask, PostgreSQL}{}
\resumeItemListStart
\resumeItem{Built a full-stack MVC E-Commerce platform utilizing Python and Flask with PostgreSQL to manage products, customers, and orders. Secured user authentication and authorization with Flask-Login; payment processing integrated via Stripe API.}
\resumeItem{Deployed on Heroku, supporting a $~70$-user base; optimized backend performance through asynchronous database queries and Flask's request handling, reducing response times by 35\%.}
\resumeItemListEnd

% Crypto Prediction ML Model
\resumeProjectHeading
{\href{https://github.com/knightwayne/}{\underline{\textbf{Crypto Prediction ML Model}}} | TensorFlow, PyTorch, scikit-learn, FastAPI, Docker, React, Pandas, gRPC}{}
\resumeItemListStart
\resumeItem{Deployed containerized ML model as a RESTful service using FastAPI, trained with LSTM and gradient boosting on over 1 million crypto trading records/day; feature engineering included moving averages, volatility, and momentum indicators.}
\resumeItem{Exposed model via low-latency gRPC endpoints (~500ms inference time) with Flask backend, integrated into a React dashboard for visualization and real-time predictions.}
\resumeItemListEnd

% TCP P2P File Transfer
\resumeProjectHeading
{\href{https://github.com/knightwayne/Mini-Dropbox-Simulator}{\underline{\textbf{Langarian TCP P2P File Transfer}}} | C/C++, POSIX, Socket Programming}{}
\resumeItemListStart
\resumeItem{Built TCP-based P2P file sharing application using C and POSIX sockets, enabling recursive synchronization with server similar to Dropbox.}
\resumeItem{Achieved transfer throughput of 20MB/s for files over 1GB in size, implementing parallel socket connections; managed 10 sockets per client for concurrency.}
\resumeItemListEnd

\resumeSubHeadingListEnd  % End the main list

\end{document}